Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-20 2015-turklang-kazdep/paper.tex
output
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60905 72bbbca6-d526-0410-a7d9-f06f51895060

\usepackage{polyglossia}
\setdefaultlanguage[variant=australian]{english}

@@

>>>>

\usepackage{alltt}
\usepackage{polyglossia}
\setdefaultlanguage[variant=australian]{english}

@@

\begin{figure}
\begin{tiny}
\begin{alltt}
"<Елде>"
        "ел" n loc
"<ағылшын>"
        "ағылшын" n nom
"<үстемдігіне>"
        "үстемдік" n px3sp dat
"<қарсы>"
        "қарсы" post
"<жаңа>"
        "жаңа" adj
"<толқулар>"
        "толқу" n pl nom
"<басталды>"
        "баста" v tv pass ifi p3 pl
"<.>"
        "." sent
\end{alltt}
\end{tiny}
\caption{Example output after preprocessing and manual disambiguation. Each token is annotated for lemma,
   part of speech and morphosyntactic information.}
\end{figure}
